A Case Study in Preserving a High Energy Physics Application

### 2014-03-13 paper.tex
table bold format + capatilization

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 180.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

The final data analysis, investigated below, can be run as a single
process, and contains a stringent event selection to keep only high
quality candidate events for the underlying physical process (using
about 20$\,$MiB of space).  Quantities from the selected events can be
both plotted and used in multivariate analysis to determine the level
of expected signal in real data.
This package is written using the CMSSW build framework,
but only utilizes code from ROOT,
a particle physics toolkit underlying CMSSW,
and a few external python dependencies for convenience.
The latter have to be manually fetched and installed,
while the analysis program is built by CMSSW after being checked out of git.

@@

\subsection{Workflow of Matthias's Example}

The workflow of Matthias's exmaple can be divided into eight procedures.

@@

(g) Install grid control ~\cite{holtman2001cms}, obtain CMS data from grid and store the data into HDFS ~\cite{borthakur2008hdfs} mounted as one local file system.

@@

Figure~\ref{fig:dependencies} illustrates all the dependencies
involved in the program, which can be divided into two categories: clear
dependencies and implicit dependencies. Clear dependencies include scientific data
dependencies and direct software dependencies which can be extracted directly
from the analysis program. The scientific data of this example comes from the Grid. Direct software dependencies include CMSSW, Git, HTTP and one personal home page.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
        {\tt scram b -j32} \\
        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
        {\tt set {\bf GIT} = (\url{https://github.com})} \\
        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

In order to repeat Matthais's example, we consulted the original
author by email about the necessary work for the experiment. In response,
Matthias introduced the general workflow of his tau roast program through one long
email including notes, linux shell commands, web linksi, as illustrated by the Version 1 of
Table~\ref{table:scripts}.

However, this solution to repeat one experiment has three potential drawbacks.
Firstly, the experience of repeating one tau roast program through emails is
chaotic. You need to constantly jump around multiple web links. There are overlap
between the content of the email and the content of web links, which needs the
new user to merge them. Multiple communication through emails is necessary to
ensure the successful reproduction of the whole analysis. For example, the original
email refers to one environment variable called CMSSW\_base without clear
declaration, the new user needs to send one email to the original writer to
obtain its accurate value. Secondly, the necessary procedures to repeat the
experiment, including software acquisition from different sources, is complex
for the new user. In Matthias's example, the sources of software includes
CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
user of CMSSW. What's more, some parts of the workflow are unrepeatable. The
third step of this experiment requires the new user to own the access authority
of the Grid and involves the analysis of AOD data with the size of about 400TB.

@@

\subsection{Solution 2: Script} One possible solution for the access authority
problem of grid data is to grant the new user the authority to access gird data
directly. Another possible solution is let the new user directly operate on the
machine the original author used. As for the complexity of jumping between
multiple web links, people may suggest that the original author
should generate one script including all the contents from different web links.

To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, software acquisition from CMSSW, Git and other web resources, and software installation, ends with the execution of the actual analysis program. Version 2 of Table~\ref{table:scripts} illstrates the merged script. As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a grid certification.

@@

So far, the data access authority is ignored and
the reproduction of the experiment is on the machine the original author used. 
As for grid data, using the data
copy stored in the machine where Matthias executed the experiment requires the
new user to have the authority to access the machine, which complicates the
management of the original machine, even is impossible if the original machine
executes rigid user access control. Granting everyone who wants to repeat the
analysis the access authority for grid is unacceptable to system administrator.

@@

Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package. 
One reason is that figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and Matthias is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Archive Path & Service Description \\ \hline
        {\tt /archive/OS/path} & OS Image \\ \hline
        {\tt /archive/software/path} & Common Software Library \\ \hline
        {\tt /archive/CMSSW/path} & CMS Software Library \\ \hline
        {\tt /archive/git/path} & Git Software Library \\ \hline
        {\tt /archive/http/path} & http resources \\ \hline
        {\tt /archive/experiment/path} & experiment private files \\ \hline
        {\tt /archive/grid-data/path} & data from the Grid \\ \hline
    \end{tabular}
    \caption{Structure Organization of the Archive}
    \label{table:archive-map}
\end{table}

@@

The section introduces our implementation of one fine-grained packaging utility based on Solution 4. With the help of one
virtual filesystem access tool, Parrot, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.

@@

Parrot is a virtual filesystem access tool which attaching existing programs to
a variety of remote {\tt I/O} systems including http, ftp, gridftp, irods, HDFS,
xrootd, grow and chirp. It traps all system calls of one program through ptrace
debugging interface, and replaces them with remote {\tt I/O} operations as desired.
Through executing one program under Parrot, all the paths of files involved in
this program can be recorded.

With the help of Parrot, one packaging utility which generates one independent
package for one program to make the reproduction of the program convenient can
be deployed. The starting point of the packaging utility is one successful execution
sandbox (the data from grid has been preserved in HDFS and the software from
CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
data analysis code under Parrot and get the name list of all the files actually
accessed during the execution process of the actual data analysis. Then,
according to the filename list, one package containing all the necessary data
and software for one analysis program is generated. Next time, when another
scholar wants to repeat the program, he only needs to obtain the package and
directly execute the actual analysis program inside the package. 
Figure~\ref{fig:solution3} illustrates the working principle of the packaging utility.

@@

(1) execute one analysis program under Parrot and obtain filename list (L1) of it

@@

The command used to generate the filename list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.

{\tt parrot\_run -L namelist /bin/tcsh script\_v4.sh}

The original ouput of this command is one namelist file with the size of 6.6MB
and 132,058 lines, each of which corresponds to one one accessed file of the
program. We noticed that some items appeared multiple times in the filename list. To reduce the
packaging time, de-duplication and sorting techoniques are used for the
namelist file, generating one smaller file with the size of 3.2MB and 67,178 lines.

(2) generate one package containing the files of L1

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
     the total size of package&21GB \\ \hline
    the total number of files&15905\\ \hline
    the total number of directory&1549\\ \hline
    the total number of symbolic link&4614 \\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Path used in Program & Actual Location \\ \hline
    {\tt /} & {\tt /tmp/package-hep} \\ \hline
    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
    {\tt /dev} & {\tt /dev} \\ \hline
    {\tt /misc} & {\tt /misc}\\ \hline
    {\tt /net} & {\tt /net}\\ \hline
    {\tt /proc} & {\tt /proc}\\ \hline
    {\tt /sys} & {\tt /sys}\\ \hline
    {\tt /var} & {\tt /var}\\ \hline
    {\tt /selinux} & {\tt /selinux}\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

%*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux
(3) rerun the analysis program using the package

When another scholar wants to repeat the analysis program, 
the description of the exepriment environment is firstly referred to build the underlying OS and basic software environment. In this example, the only necessary software basis is Parrot. Then the scholar can obtain one copy of the package and its map file, and rerun the program using the following command:

@@

Under Solution 4, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction only needs
to set necessary environment variables, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

@@

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & user manual of package \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table*}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    Machine & Kernel & Distro & CPU & Mem\\ 
    Type & Version & Version & Cores & (GB)\\ \hline
    earth  & 2.6.18-371.4.1.el5 & RedHat 5.10 & 64 & 125 \\ \hline 
    local VM& 2.6.18-371.4.1.el5 & CentOS 5.10 & 4 & 2 \\ \hline
    EC2 VM& 2.6.18-348.el5xen & RedHat 5.9 & 16 & 60.5 \\ \hline
    \end{tabular}
    \caption{Configuration of Different Machines}
    \label{table:config-vm}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Sub-Task & Time & Percentage \\ \hline
    Software acquisition from CMSSW & 7min 24s & 21.44\% \\ \hline
    Software acquisition from Git & 9s & 0.43\% \\ \hline
    Software acquisition from Wget & 38s & 1.83\% \\ \hline
    Environment Build - SCRAM & 5min 48s & 16.80\% \\ \hline
    Environment Build - Python & 1s & 0.05\% \\ \hline
    Data analysis & 20min 31s & 59.44\% \\ \hline
    Total & 34min 31s & 100.00\% \\ \hline
    \end{tabular}
    \caption{Breakdown of Execution Time of Solution 2}
    \label{table:time-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data Size \\ \hline
    Software from CMSSW & 448.3MB \\ \hline
    Software from Git & 73.7MB \\ \hline
    Software from Wget & 52MB \\ \hline
    HDFS & 43.3GB \\ \hline
    Total & 43.86GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 2}
    \label{table:datasize-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Sub-Task & Time \\ \hline
    Obtain file namelist & 28min 23s \\ \hline
    Generate P1 & 85min 51s \\ \hline
    Re-run the program within P1 & 13min 4s \\ \hline
    \end{tabular}
    \caption{Time Breakdown of Solution 4}
    \label{table:time-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|r|}
    \hline
    Data Category &Location & Data Size \\ \hline
    HDFS & hadoop &20GB \\ \hline
    PanFS & pscratch & 1.6MB \\ \hline
    CVMFS & cvmfs &103MB \\ \hline 
    NFS & opt &53KB \\ \hline
    AFS & afs &34MB \\ \hline
    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
    Total & &21GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Machine Type & Execution Time \\ \hline
    earth & 13min 4s \\ \hline
    EC2 VM & 13min 30s\\ \hline
    local VM & 21min 38s \\ \hline
    \end{tabular}
    \caption{Execution Time on Different Machines}
    \label{table:time-vm}
\end{table}

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & HDFS& 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 51MB & 51MB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 180.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

The final data analysis, investigated below, can be run as a single
process, and contains a stringent event selection to keep only high
quality candidate events for the underlying physical process (using
about 20$\,$MB of space).  Quantities from the selected events can be
both plotted and used in multivariate analysis to determine the level
of expected signal in real data.
This package is written using the CMSSW build framework,
but only utilizes code from ROOT,
a particle physics toolkit underlying CMSSW,
and a few external python dependencies for convenience.
The latter have to be manually fetched and installed,
while the analysis program is built by CMSSW after being checked out of git.

@@

\subsection{Workflow of the Example}

The workflow of the exmaple can be divided into eight procedures.

@@

(g) Install grid control ~\cite{holtman2001cms}, obtain CMS data from Grid and store the data into HDFS ~\cite{borthakur2008hdfs} mounted as one local file system.

@@

Figure~\ref{fig:dependencies} illustrates all the dependencies
involved in the program, which can be divided into two categories: clear
dependencies and implicit dependencies. Clear dependencies include scientific data
dependencies and direct software dependencies which can be extracted directly
from the analysis program. The scientific data of this example comes from the Grid ~\cite{holtman2001cms}. Direct software dependencies include CMSSW, Git, HTTP and one personal home page.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
        {\tt scram b -j32} \\
        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
        {\tt setenv {\bf GIT} \url{https://github.com}} \\
        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
        {\tt setenv {\bf GIT} \url{https://github.com}} \\
        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

In order to repeat Matthais's example, we consulted the original
author by email about the necessary work for the experiment. In response,
the original author introduced the general workflow of his tau roast program through one long
email including notes, linux shell commands, web linksi, as illustrated by the Version 1 of
Table~\ref{table:scripts}.

However, this solution to repeat one experiment has three potential drawbacks.
Firstly, the experience of repeating one tau roast program through emails is
chaotic. You need to constantly jump around multiple web links. There are overlap
between the content of the email and the content of web links, which needs the
new user to merge them. Multiple communication through emails is necessary to
ensure the successful reproduction of the whole analysis. For example, the original
email refers to one environment variable called CMSSW\_base without clear
declaration, the new user needs to send one email to the original writer to
obtain its accurate value. Secondly, the necessary procedures to repeat the
experiment, including software acquisition from different sources, is complex
for the new user. In the example, the sources of software includes
CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
user of CMSSW. What's more, some parts of the workflow are unrepeatable. The
third step of this experiment requires the new user to own the access authority
of the Grid and involves the analysis of AOD data with the size of about 400TB.

@@

\subsection{Solution 2: Script} One possible solution for the access authority
problem of Grid data is to grant the new user the authority to access gird data
directly. Another possible solution is let the new user directly operate on the
machine the original author used. As for the complexity of jumping between
multiple web links, people may suggest that the original author
should generate one script including all the contents from different web links.

To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, software acquisition from CMSSW, Git and other web resources, and software installation, ends with the execution of the actual analysis program. Version 2 of Table~\ref{table:scripts} illstrates the merged script. As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a Grid certification.

@@

So far, the data access authority is ignored and
the reproduction of the experiment is on the machine the original author used. 
As for Grid data, using the data
copy stored in the machine where the original author executed the experiment requires the
new user to have the authority to access the machine, which complicates the
management of the original machine, even is impossible if the original machine
executes rigid user access control. Granting everyone who wants to repeat the
analysis the access authority for Grid is unacceptable to system administrator.

@@

Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package. 
One reason is that figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
        \hline
        \bf Archive Path & \bf Service Description \\ \hline
        {\tt /archive/OS/path} & OS Image \\ \hline
        {\tt /archive/software/path} & Common Software Library \\ \hline
        {\tt /archive/CMSSW/path} & CMS Software Library \\ \hline
        {\tt /archive/git/path} & Git Software Library \\ \hline
        {\tt /archive/http/path} & HTTP resources \\ \hline
        {\tt /archive/experiment/path} & experiment private files \\ \hline
        {\tt /archive/grid-data/path} & data from the Grid \\ \hline
    \end{tabular}
    \caption{Structure Organization of the Archive}
    \label{table:archive-map}
\end{table}

@@

The section introduces our implementation of one fine-grained packaging utility based on Solution 4. With the help of one
virtual filesystem access tool, Parrot ~\cite{thain2005parrot}, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.

@@

Parrot is a virtual filesystem access tool which attaching existing programs to
a variety of remote {\tt I/O} systems including 
HTTP, FTP, GridFTP, iRODS, HDFS, XRootD, GROW, and Chirp. It traps all system calls of one program through ptrace
debugging interface, and replaces them with remote {\tt I/O} operations as desired.
Through executing one program under Parrot, all the paths of files involved in
this program can be recorded.

With the help of Parrot, one packaging utility which generates one independent
package for one program to make the reproduction of the program convenient can
be deployed. The starting point of the packaging utility is one successful execution
sandbox (the data from Grid has been preserved in HDFS and the software from
CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
data analysis code under Parrot and get the name list of all the files actually
accessed during the execution process of the actual data analysis. Then,
according to the filename list, one package containing all the necessary data
and software for one analysis program is generated. Next time, when another
scholar wants to repeat the program, he only needs to obtain the package and
directly execute the actual analysis program inside the package. 
Figure~\ref{fig:solution3} illustrates the working principle of the packaging utility.

@@

{\bf(1)} Execute one analysis program under Parrot and obtain filename list (L1) of it

@@

The command used to generate the filename list is as follows. The {\tt name-list} parameter refers to the path of the file containing all the accessed file name of the experiment.

{\tt parrot\_run \texttt{-{}-}name-list namelist /bin/tcsh script\_v4.sh}

The original ouput of this command is one namelist file with the size of 6.6MB
and 132,047 lines, each of which corresponds to one one accessed file of the
program. We noticed that some items appeared multiple times in the filename list. To reduce the
packaging time, de-duplication and sorting techoniques are used for the
namelist file, generating one smaller file with the size of 3.2MB and 67,168 lines.

{\bf (2)} Generate one package containing the files of L1

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
    \hline
     the total size of package: 21GB \\ 
    the total number of files: 15905\\ 
    the total number of directory: 1549\\ 
    the total number of symbolic link: 4614 \\ \hline 
    \end{tabular}
    \caption{Package Infomation}
    \label{table:package-info}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \bf Path used in Program & \bf Actual Location \\ \hline
    {\tt /} & {\tt /tmp/package-hep} \\ \hline
    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
    {\tt /dev} & {\tt /dev} \\ \hline
    {\tt ...} & {\tt ...}\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

%*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux
{\bf (3)} Repeat the analysis program using the package

When another scholar wants to repeat the analysis program, 
the description of the exepriment environment is firstly referred to build the underlying OS and basic software environment. In this example, the only necessary software basis is Parrot. Then the scholar can obtain one copy of the package and its map file, and rerun the program using the following command. The {\tt m} parameter can be used to refer to the path of map file, which will be explained in the next part.

@@

Under Solution 4, the reproduction of one analysis program becomes easier.
Rethink the example, the reproduction only needs
to set necessary environment variables, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

@@

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        \bf Solution ID & \bf Data Resources &\bf Software Resources & \bf Operation Manual \\ \hline
        Solution 1& Grid & CMSSW Git HTTP & email \\ \hline
        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & user manual of package \\ \hline
    \end{tabular}
    \caption{Relationship of Different Solutions}
    \label{table:relationship}
\end{table*}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    \bf Machine & \bf Kernel Version & \bf Distro & \bf CPU & \bf Mem\\ 
    \bf Type &  & \bf Version & \bf Cores & (\bf GB)\\ \hline
    earth  & 2.6.18-371.4.1.el5 & RedHat 5.10 & 64 & 125 \\ \hline 
    local VM& 2.6.18-371.4.1.el5 & CentOS 5.10 & 4 & 2 \\ \hline
    EC2 VM& 2.6.18-348.el5xen & RedHat 5.9 & 16 & 60.5 \\ \hline
    \end{tabular}
    \caption{Configuration of Different Machines}
    \label{table:config-vm}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Sub-Task & \bf Time & \bf Percentage \\ \hline
    Obtain software from CMSSW & 7min 24s & 21.44\% \\ \hline
    Obtain software from Git & 9s & 0.43\% \\ \hline
    Obtain software from Wget & 38s & 1.83\% \\ \hline
    Environment build - SCRAM & 5min 48s & 16.80\% \\ \hline
    Environment build - Python & 1s & 0.05\% \\ \hline
    Data analysis & 20min 31s & 59.44\% \\ \hline
    Total & 34min 31s & 100.00\% \\ \hline
    \end{tabular}
    \caption{Breakdown of Execution Time of Solution 2}
    \label{table:time-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    \bf Data Category & \bf Data Size \\ \hline
    Software from CMSSW & 448.3MB \\ \hline
    Software from Git & 73.7MB \\ \hline
    Software from Wget & 52MB \\ \hline
    HDFS & 43.3GB \\ \hline
    Total & 43.86GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 2}
    \label{table:datasize-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    \bf Sub-Task &\bf Time \\ \hline
    Obtain file namelist & 28min 23s \\ \hline
    Generate P1 & 85min 51s \\ \hline
    Re-run the program within P1 & 13min 4s \\ \hline
    \end{tabular}
    \caption{Time Breakdown of Solution 4}
    \label{table:time-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|r|}
    \hline
    \bf Data &\bf Location & \bf Data \\ 
    \bf Category & & \bf Size\\ \hline
    HDFS & hadoop &20GB \\ \hline
    PanFS & pscratch & 1.6MB \\ \hline
    CVMFS & cvmfs &103MB \\ \hline 
    NFS & opt &53KB \\ \hline
    AFS & afs &34MB \\ \hline
    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
    Total & &21GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    \bf Machine Type & \bf Execution Time \\ \hline
    earth & 13min 4s \\ \hline
    EC2 VM & 13min 30s\\ \hline
    local VM & 21min 38s \\ \hline
    \end{tabular}
    \caption{Execution Time on Different Machines}
    \label{table:time-vm}
\end{table}
